\thetitle

### 2020-11-18 sun_phases/spin_qudit_tomo.tex
minor cleanup and notation changes

The remainder of this section is devoted to defining $\epsilon_V^2$, which is derived in Appendix \ref{sec:error}, and can be skipped without consequence for the discussions in the rest of this paper.
To write out the quantum error scale $\epsilon_V^2$ explicitly, we define a matrix of structure constants
\begin{align}
  g_{L\ell} \equiv \sum_{m,n=-\ell}^\ell
  \obk{T_{L,m+n}|T_{\ell m}T_{\ell n}} \op{m}{n},
\end{align}
and the inversion operator $\I\equiv\sum_m\p{-1}^m\op{-m}{m}$, which are used to define the $\p{2\ell+1}$-component vectors
\begin{align}
  \ket{\chi_{VL}}
  &\equiv \sum_{M=-L}^L \chi^V_{LM} \ket{M}, \\
  \chi^V_{Lm} &\equiv \sum_\ell \obk{\N_{V\ell}|\D_M|\I g_{L\ell}}, \\
  \D_M &\equiv \sum_{m,m'} \delta_{M,m'-m} \op{mm'}.
\end{align}
Here $\D_M$ simply picks off the $M$-th diagonal of the matrix it acts on, such that $\obk{\N_{V\ell}|\D_M|\I g_{L\ell}}$ is an inner product between the $M$-th diagonals of $\N_{V\ell}$ and $\I g_{L\ell}$.
We then define
\begin{align}
  \L_{V\ell} \equiv \N_{V\ell} + \I\N_{V\ell}\I,
\end{align}
in terms of which we have that $\epsilon_V^2 \equiv \sum_\ell \epsilon_{V\ell}^2$, with
\begin{align}
  \epsilon_{V\ell}^2 \equiv
  \bk{\chi_{V\ell}|\p{\L_{V\ell}^{-1}
      - \L_{V\ell}^{-1}\N_{V\ell}\L_{V\ell}^{-1}}|\chi_{V\ell}}.
\end{align}

>>>>

The remainder of this section is devoted to defining the quantum error scale $\epsilon_V^2$ (derived in Appendix \ref{sec:error}), and can be skipped without consequence for the discussions in the rest of this paper.
To write out $\epsilon_V^2$ explicitly, we define a matrix of structure constants
\begin{align}
  g_{L\ell} \equiv \sum_{m,n=-\ell}^\ell
  \obk{T_{L,m+n}|T_{\ell m}T_{\ell n}} \op{m}{n},
\end{align}
and the inversion operator $\I\equiv\sum_m\p{-1}^m\op{-m}{m}$, which are used to define the $\p{2\ell+1}$-component vectors
\begin{align}
  \ket{\chi_{V\ell}}
  &\equiv \sum_{m=-\ell}^\ell \chi^V_{\ell m} \ket{m}, \\
  \chi^V_{LM} &\equiv \sum_\ell \obk{\N_{V\ell}|\D_M|\I g_{L\ell}}, \\
  \D_M &\equiv \sum_{m,m'} \delta_{M,m'-m} \op{mm'}.
\end{align}
Here $\D_M$ simply picks off the $M$-th diagonal of the matrix it acts on, such that $\obk{\N_{V\ell}|\D_M|\I g_{L\ell}}$ is an inner product between the $M$-th diagonals of $\N_{V\ell}$ and $\I g_{L\ell}$.
The vectors $\ket{\chi_{V\ell}}$ allow us to express reconstruction error in the simple form
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \sp{\bk{\chi_{V\ell}|\rho_\ell}
    - \bk{\rho_\ell|\N_{V\ell}|\rho_\ell}},
\end{align}
where $\ket{\rho_\ell}\equiv\sum_m \rho_{\ell m}\ket{m}$.
This error is straightforward to maximize with respect to all states $\rho$, which yields the bound in Eq.~\eqref{eq:bound} with $\epsilon_V^2 \equiv \sum_\ell \epsilon_{V\ell}^2$ and
\begin{align}
  \epsilon_{V\ell}^2 \equiv
  \bk{\chi_{V\ell}|\p{\L_{V\ell}^{-1}
      - \L_{V\ell}^{-1}\N_{V\ell}\L_{V\ell}^{-1}}|\chi_{V\ell}},
\end{align}
where
\begin{align}
  \L_{V\ell} \equiv \N_{V\ell} + \I\N_{V\ell}\I.
\end{align}
